---
output: 
  html_document:
    include:
      after_body: footer.html
knit: (function(inputFile, encoding) { 
      out_dir <- 'docs';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'index.html')) })
editor_options: 
  chunk_output_type: console
---


###  The Andic Dictionaries Examples Database {.tabset .tabset-fade .tabset-pills}

[![DOI]

In this database linguistic examples are collected from various dictionaries of Andic languages. This database is based on [the Comparative Andic dictionary database](https://github.com/phon-dicts-project/comparative_andic_dictionary_database). Some characters may be displayed incorrectly.
At the moment some entries may lack actual instances of usage.

Download database: [.csv](https://raw.githubusercontent.com/LingConLab/andic_dictionary_examples_database/main/andic_examples.csv)

```{r setup, include=FALSE, warning=F}
knitr::opts_chunk$set(echo=FALSE, message=FALSE)
library(tidyverse)

db <- read_csv('andic_examples.csv') %>% 
  select(-c(id_word,id_meaning,id))

```


```{r warning=F}
db %>% 
  select(-reference) %>% 
  DT::datatable(filter = 'top', rownames = FALSE, options = list(pageLength = 20, dom = 'tip'), escape = FALSE)
```

# References
- Alekseev, M.E., & Azayev H.G. (2019). *Botlixsko-russkij slovar’ [Botlikh-Russian dictionary]*. Moscow: Academia.
- Magomedova, P. T. (1999). *Čamalinsko-russkij slovarʹ [Chamalal-Russian dictionary]*. Makhachkala: IJaLI.
- Magomedova, P. T. (2003). *Tindinsko-russkij slovarʹ [Tindi-Russian dictionary]*. Makhachkala: IJaLI.
- Magomedova, P. T. (2004). *Bagvalinsko-russkij slovarʹ [Bagvalal-Russian dictionary]*. Makhachkala: IJaLI.
- Magomedova, P. T., & Abdulaeva, I. A. (2007). *Axvaxsko-russkij slovarʹ [Akhvakh-Russian dictionary]*. Makhachkala: IJaLI.
- Magomedova, P. T., & Xalidova, R. Š. (2001). *Karatinsko-russkij slovarʹ [Karata-Russian dictionary]*. Makhachkala: IJaLI.
- Saidova, P. A. (2006). *Godoberinsko-russkij slovarʹ [Godoberi-Russian dictionary]*. Makhachkala: DNC RAN Institut jazyka, literatury i iskusstva im. G. Cadasy i Institut évoljucionnoj antropologii im. M. Planka.
- Saidova, P. A., & Abusov, M. G. (2012). *Botlixsko-russkij slovarʹ [Botlikh-Russian dictionary]*. Makhachkala: DNC RAN Institut jazyka, literatury i iskusstva im. G. Cadasy i Institut évoljucionnoj antropologii im. M. Planka.
