---
title: "The Andic Dictionaries Examples Database"
format: html
output-file: "index.html"
include-after-body: "footer.html"
execute: 
  warning: false
  echo: false  
page-layout: full
doi: 10.5281/zenodo.7793144
---
In this database linguistic examples are collected from various dictionaries of the Andic languages. This database is based on [the Comparative Andic dictionary database](https://github.com/phon-dicts-project/comparative_andic_dictionary_database). [Download full database in .csv format.](https://raw.githubusercontent.com/LingConLab/andic_dictionary_examples_database/main/andic_examples.csv)

To search for words with the *Cyrillic palochka* you can use Latin uppercase "I", digit "1", exclamation mark "!" or the uppercase palochka itself ("Ӏ"). For "ᴴ" you can type Cyrillic "н". Accents are neutralized, e.g. you can search for letters like "ā" by typing just "a". Note that regular expressions are supported (e.g., "." stands for any symbol, ".*" - any symbol zero or more times, ".+" - any symbol 1 or more times).

With the corresponding buttons below you can copy, export to *.csv* or *.xlsx* the currently filtered table.


```{r setup}
#| include: false
library(tidyverse)
library(DT)
# ids originated from andic dictionary db: https://github.com/phon-dicts-project/comparative_andic_dictionary_database
db <- read_csv('andic_examples.csv') %>% 
  select(-c(id_word,id_meaning,id,comment))
```

```{r}
db %>% 
  datatable(filter = 'top',
            extensions = 'Buttons',
            plugins = "accent-neutralise", # works with BOTH "comibining acute accent" with cyrillic and combining macron
            rownames = F,
            options = list(pageLength = 15, 
                           dom = 'Btip',
                           buttons = c('copy','csv','excel'),
                           initComplete = JS(readLines("character_map.js"))))
```

## References

- Alekseev, M.E., & Azayev H.G. (2019). *Botlixsko-russkij slovar’ [Botlikh-Russian dictionary]*. Moscow: Academia.
- Magomedova, P. T. (1999). *Čamalinsko-russkij slovarʹ [Chamalal-Russian dictionary]*. Makhachkala: IJaLI.
- Magomedova, P. T. (2003). *Tindinsko-russkij slovarʹ [Tindi-Russian dictionary]*. Makhachkala: IJaLI.
- Magomedova, P. T. (2004). *Bagvalinsko-russkij slovarʹ [Bagvalal-Russian dictionary]*. Makhachkala: IJaLI.
- Magomedova, P. T., & Abdulaeva, I. A. (2007). *Axvaxsko-russkij slovarʹ [Akhvakh-Russian dictionary]*. Makhachkala: IJaLI.
- Magomedova, P. T., & Xalidova, R. Š. (2001). *Karatinsko-russkij slovarʹ [Karata-Russian dictionary]*. Makhachkala: IJaLI.
- Saidova, P. A. (2006). *Godoberinsko-russkij slovarʹ [Godoberi-Russian dictionary]*. Makhachkala: DNC RAN Institut jazyka, literatury i iskusstva im. G. Cadasy i Institut évoljucionnoj antropologii im. M. Planka.
- Saidova, P. A., & Abusov, M. G. (2012). *Botlixsko-russkij slovarʹ [Botlikh-Russian dictionary]*. Makhachkala: DNC RAN Institut jazyka, literatury i iskusstva im. G. Cadasy i Institut évoljucionnoj antropologii im. M. Planka.
